Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-15 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}.
        \begin{itemize}
            \item Most of the recent work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}.
        \begin{itemize}
            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
        \end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services
        \item Goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}
        \begin{itemize}
            \item Most of the recent work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}
        \begin{itemize}
            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
        \end{itemize}
